The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-14 analysis/paper/paper.qmd
Update comments in data reading code

# Read thesis metadata ----
## All theses
theses_all <-
  readxl::read_xlsx(path = here("analysis", "data", "raw_data", "theses-all.xlsx"))

## Theses with PDF available
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(data_path, pattern = "*.pdf")

emu_theses <- 
  read_csv(here(data_path, "theses-metadata.csv")) %>%
  mutate(text = "") %>%
  filter(!is.na(pdf_via))

@@

```{r}
#| label: extract-pdf-text
#| echo: false
emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

In order to describe the legacy of the EMU program, including the distinctive features of its didactic approach, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: `r nrow(theses_all)` theses with an average of `r mean(str_length(emu_theses$text_clean), na.rm = TRUE)` words produced over the years for the duration of the program between `r paste0(min(theses_all$grad_year, na.rm = TRUE), "-", max(theses_all$grad_year, na.rm = TRUE))`. The first year of the program was not represented, as PDF files were only available from 2008 onward.

>>>>

# Read thesis metadata ----
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(data_path, pattern = "*.pdf")

## Read metadata for all theses
all_theses <-
  readxl::read_xlsx(path = here(data_path, "theses-all.xlsx"))

## Read only metadata for theses with PDF available
emu_theses <- 
  read_csv(here(data_path, "theses-metadata.csv")) %>%
  mutate(text = "") %>%
  filter(!is.na(pdf_via))

@@

```{r}
#| label: extract-pdf-text
#| echo: false

# Extract text from PDFs
# On the first run, this function might take extra time as a Python environment needs to be set up
emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

In order to describe the legacy of the EMU program, including the distinctive features of its didactic approach, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: `r nrow(all_theses)` theses with an average of `r mean(str_length(emu_theses$text_clean), na.rm = TRUE)` words produced over the years for the duration of the program between `r paste0(min(all_theses$grad_year, na.rm = TRUE), "-", max(all_theses$grad_year, na.rm = TRUE))`. The first year of the program was not represented, as PDF files were only available from 2008 onward.
